---
title: "Untitled"
author: "CW"
date: "18/08/2021"
output: html_document
---

```{r}
tuesdata <- tidytuesdayR::tt_load('2020-11-03')
tuesdata <- tidytuesdayR::tt_load(2020, week = 45)
```
```{r}
library(tidyverse)
library(tidytuesdayR)
library(scales)
library(ggplot2)
```
```{r Load}

tt <- tt_load("2020-11-03")

```
```{r}
tt$ikea
```
```{r}
ikea <- tt$ikea %>% 
  select(-X1) %>% 
  mutate(price_usd = 0.27 * price)

ikea %>% 
  view
```

```{r}
ikea %>% 
  count(category, sort = TRUE) %>% 
  mutate(category = fct_reorder(category, n)) %>% 
  ggplot(aes(n, category)) +
  geom_col()
```

```{r}
ikea %>% 
  count(category, sort = TRUE) %>% 
  mutate(category = fct_reorder(category, n)) %>% 
  ggplot(aes(n, category)) +
  geom_col() +
  labs(x = "number of items",
       y = "",
       title = "Most Common Categories of IKEA Items")
```

```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot()
```
```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  scale_x_log10()
```
# up to 6.53 
# https://www.youtube.com/watch?v=lY0YLDZhT88

```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  geom_point(aes())+
  scale_x_log10()
```
```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .5)+
  scale_x_log10()
```



```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .2)+
  scale_x_log10()
```

```{r}
ikea %>% 
  mutate(category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10()
```

```{r}
library(glue)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10()
```
```{r}
library(glue)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price)) %>% 
  ggplot(aes(price, category)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10()
```


```{r}
library(glue)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10()
```
```{r}
library(glue)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```


# up to 11:43
# https://www.youtube.com/watch?v=lY0YLDZhT88



```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")

```

#below with no log - the above is better as more suited to normal distribution; as some are bimodal better than a box plot
# but for completeness ahve shown this

```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")

```

```{r}
ikea %>% 
count(other_colors, sort = TRUE)
```

```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category, fill = other_colors)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```
#make transparent

```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category, fill = other_colors)) +
  geom_density_ridges(alpha = .5) +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

#other colours more expensive.  therefore predictive model could include that
#up to 16:47 https://www.youtube.com/watch?v=lY0YLDZhT88

```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category, fill = other_colors)) +
  geom_boxplot() +
  #geom_density_ridges(alpha = .5) +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

If we were building a predictive model, we'd probably include both category and other_colors but also consider volume


```{r}
library(ggridges)

ikea %>% 
  add_count(category, name = "category_total") %>% 
  mutate(category = glue("{ category } ({ category_total })"),
        category = fct_reorder(category, price_usd)) %>% 
  ggplot(aes(price_usd, category, fill = other_colors)) +
  geom_density_ridges(alpha = .5) +
  # geom_jitter(width = 0, height = .1, alpha = .25)+
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

volume

```{r}
ikea %>% 
  count(name, sort = TRUE)
```

```{r}
ikea %>% 
  count(name,category, sort = TRUE)
```

```{r}
ikea %>% 
  count(name,category, designer, sort = TRUE)
```

```{r}
ikea %>% 
  count(name,category, designer, sort = TRUE) %>% View()
```

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum)) %>% 
  ggplot(aes(n, name, fill = category, )) +
  geom_col()
```

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum)) %>% 
  ggplot(aes(n, name, fill = category, )) +
  geom_col()
```


```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum)) %>% 
  ggplot(aes(n, name, fill = category, )) +
  geom_col()
```

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum), 
         category = fct_reorder(category, n, sum)) %>%
  ggplot(aes(n, name, fill = category, )) +
  geom_col() +
  labs(x = "# of items",
       y = "Name of item")
```

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, -n, sum), 
         category = fct_reorder(category, n, sum)) %>%
  ggplot(aes(n, name, fill = category, )) +
  geom_col() +
  labs(x = "# of items",
       y = "Name of item")
```

note can put negative sign in to flip the order like above

```{r}
ikea %>% 
  mutate(name = fct_lump(name, 20)) %>% 
  filter(name != "Other") %>% 
  count(name,category, sort = TRUE) %>% 
  mutate(name = fct_reorder(name, n, sum), 
         category = fct_reorder(category, n, sum)) %>%
  ggplot(aes(n, name, fill = category, )) +
  geom_col() +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  labs(x = "# of items",
       y = "Name of item")
```


```{r}
ikea %>% 
  View
```

short description has text then at times numbers after the comma although not all the time,

```{r}
ikea %>% count(short_description, sort = TRUE) %>% View()
```

```{r}
ikea %>% 
  select(short_description)
```

```{r}
ikea <- tt$ikea %>% 
  select(-X1) %>% 
  mutate(price_usd = 0.27 * price, 
        short_description = str_trim(str_replace_all(short_description, "\\s+", " ")))

```

```{r}
ikea %>% 
  select(short_description) %>% 
  separate(short_description, c("main_description", "rest"),
           sep = ", ", 
           extra = "merge", 
           fill = "right") %>% 
  extract(rest, "numbers", "([\\d\\-xX]+) cm", remove = FALSE) %>% 
  View()
```


https://www.youtube.com/watch?v=lY0YLDZhT88 up to 27:52