---
title: "Analyzing regsitered nurses in R"
author: "Chris Weatherburn"
date: "09/12/2021"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---
```{r}
setwd("D:/Chris/Documents/R work/R Tidy Tuesday")
```

```{r}
library(tidyverse)
library(tidytuesdayR)
library(ggthemes)
```

```{r}
tt <- tidytuesdayR::tt_load('2021-10-05')
tt$nurses
```

#column names not in snake case convert so can analyse them

```{r}
library(scales)
library(janitor)
library(tidyverse)
theme_set(theme_light())
```

```{r}
tt$nurses %>% 
  clean_names() %>% 
  View()
```

```{r}
nurses <- tt$nurses %>% 
  clean_names()
```

```{r}
nurses %>% 
  count(state)
```

```{r}
nurses %>% 
  count(state)
```


```{r}
nurses %>% 
  count(year, wt = total_employed_rn) %>% 
  ggplot(aes(year, n)) +
  geom_col()
```

```{r}
nurses %>% 
  count(year, wt = total_employed_rn) %>% 
  ggplot(aes(year, n)) +
  geom_col() +
  labs( y = '# of registered nurses nationally')
```

```{r}
nurses %>% 
  filter(state == "New York") %>% 
  ggplot(aes(year, total_employed_rn)) +
  geom_col()
```

```{r}
nurses %>% 
  filter(state %in% c("New York", "California")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line()
```



```{r}
nurses %>% 
  filter(state %in% c("New York", "California")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line() +
  expand_limits(y = 0)

```

```{r}
nurses %>% 
  filter(state %in% c("New York", "California")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "# of employed registered nurses")

```

```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "# of employed registered nurses")

```

```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "# of employed registered nurses")
  scale_y_continuous(labels = comma_format())

```

#below in theory adds a . in the y axis label

```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania")) %>% 
  ggplot(aes(year, total_employed_rn, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "# of employed registered nurses")
scale_y_continuous(labels = comma_format(big.mark = "."))

```




```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania")) %>% 
  ggplot(aes(year, hourly_wage_median, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "Hourly wage") +
scale_y_continuous(labels = dollar_format())

```

```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania", "Michigan", "Florida")) %>% 
  ggplot(aes(year, hourly_wage_median, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "Hourly wage") +
scale_y_continuous(labels = dollar_format())

```
#note below adds the .00 to the dollar format on y axis

```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania", "Michigan", "Florida")) %>% 
  ggplot(aes(year, hourly_wage_median, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "Hourly wage") +
scale_y_continuous(labels = dollar_format(accuracy = 0.01))

```

```{r}
nurses %>% 
  filter(!is.na(hourly_wage_avg)) %>% 
  group_by(year) %>% 
  summarize(weighted_avg_wage = sum(hourly_wage_avg * total_employed_rn) / 
sum(total_employed_rn)) %>% 
  ggplot(aes(year, weighted_avg_wage)) +
  geom_line() +
  expand_limits(y = 0) +
  scale_y_continuous(labels = dollar_format())


```

#note gap in data

```{r}
nurses %>% 
  filter(!is.na(hourly_wage_avg)) %>% 
  group_by(year) %>% 
  summarize(weighted_avg_wage = sum(hourly_wage_avg * total_employed_rn) / 
sum(total_employed_rn)) %>% 
  filter(!is.na(weighted_avg_wage)) %>% 
  ggplot(aes(year, weighted_avg_wage)) +
  geom_line() +
  expand_limits(y = 0) +
  scale_y_continuous(labels = dollar_format())
```
```{r}
nurses %>% 
  filter(!is.na(hourly_wage_avg)) %>% 
  group_by(year) %>% 
  summarize(weighted_avg_wage = sum(hourly_wage_avg * total_employed_rn) / 
sum(total_employed_rn)) %>% 
  filter(!is.na(weighted_avg_wage)) %>% 
  ggplot(aes(year, weighted_avg_wage)) +
  geom_line() +
  geom_point() +
  expand_limits(y = 0) +
  scale_y_continuous(labels = dollar_format())
```
```{r}
nurses %>% 
  filter(state %in% c("New York", "California", "Texas", "Pennsylvania", "Michigan", "Florida", "Ohio", "Washington")) %>% 
  ggplot(aes(year, hourly_wage_median, color = state)) +
  geom_line() +
  expand_limits(y = 0) +
  labs(y = "Hourly wage") +
scale_y_continuous(labels = dollar_format())

```

#looking at change in hourly wages over time

```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point()


```

```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point() +
  geom_label(aes(label = state), vjust = 1, hjust = 1, check_overlap = TRUE)


```

```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point() +
  geom_text(aes(label = state), vjust = 1, hjust = 1, check_overlap = TRUE)

```

```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point(aes(size = total_employed_rn_2000)) +
  geom_text(aes(label = state), vjust = 1, hjust = 1, check_overlap = TRUE)

```

```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point(aes(size = total_employed_rn_2000)) +
  geom_text(aes(label = state), vjust = 1, hjust = 1, check_overlap = TRUE) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = percent_format())
  

```


```{r}
nurses %>% 
  filter(year %in% c(2000, 2020)) %>% 
  select(state, year, total_employed_rn, hourly_wage_median) %>% 
  pivot_wider(names_from = year, values_from = c(total_employed_rn, hourly_wage_median)) %>% 
  mutate(rn_increase = total_employed_rn_2020 / total_employed_rn_2000 - 1, 
         wage_increase = hourly_wage_median_2020 / hourly_wage_median_2000 -1) %>% 
  ggplot(aes(rn_increase, wage_increase, size = total_employed_rn_2000)) +
  geom_point(aes(size = total_employed_rn_2000)) +
  geom_text(aes(label = state), vjust = 1, hjust = 1, check_overlap = TRUE) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "% increase in # of registered nurses, 2000 to 2020",
       y = "% increase in hourly wage, 2000-2020",
       size = "# nurses 2000")
  

```

#note california increase - but not compared with change in population itself


# up to 18:53 
https://www.youtube.com/watch?v=UVmxHb2Daeo



#make a choropleth and then shiny app (choropleth is a colured map)

```{r}
map_data("state") %>% 
  as_tibble()
```


```{r}
nurses %>% 
  filter(year == 2020) %>% 
  mutate(state = str_to_lower(state)) %>% 
  inner_join(map_data("state"), by = c(state = "region")) %>% 
  ggplot(aes(long, lat, group = group)) +
  geom_polygon()

```




```{r}
nurses %>% 
  filter(year == 2020) %>% 
  mutate(state = str_to_lower(state)) %>% 
  inner_join(map_data("state"), by = c(state = "region")) %>% 
  ggplot(aes(long, lat, group = group)) +
  geom_polygon() +
  coord_map() +
  ggthemes::theme_map()
```

```{r}
nurses %>% 
  filter(year == 2020) %>% 
  mutate(state = str_to_lower(state)) %>% 
  inner_join(map_data("state"), by = c(state = "region")) %>% 
  ggplot(aes(long, lat, group = group, fill = hourly_wage_median)) +
  geom_polygon() +
  coord_map() +
  ggthemes::theme_map()
```

```{r}
nurses %>% 
  filter(year == 2020) %>% 
  mutate(state = str_to_lower(state)) %>% 
  inner_join(map_data("state"), by = c(state = "region")) %>% 
  ggplot(aes(long, lat, group = group, fill = hourly_wage_median)) +
  geom_polygon() +
  coord_map() +
  scale_fill_viridis_c(labels = dollar_format()) +
  ggthemes::theme_map() +
  labs(title = "Hourly wage of registered nurses by state, 2020", fill = "Median wage")

```
If want to know more aobut the map data this would explore it


?map_data


#below is how to interrogate other maps such as ns one

```{r}
map_data("nz") %>%  as_tibble() %>% count(region, sort = TRUE)
```

#making a shinyapp
# up to 28:58 shinyapp didn't work


